---
title: "Anorexia Nervosa: Symptom-Related Information Alters Decision-Making Policy Despite Outcome Irrelevance"
author: "Supplementary Materials"
output:
  pdf_document:
      toc: true
      toc_depth: 2
csl: apa7.csl
bibliography: ed.bib
fontsize: 12pt
linestretch: 1.1
---

```{r setup1, message = FALSE, warning = FALSE, include = FALSE, results = "hide"}
library("tidyverse")
library("shinystan")
library("emojifont")
library("patchwork")
library("ggridges")
library("viridis")
library("ellipse")
library("papaja")
library("phonR")
library("broom")
library("lme4")
library("brms")
library("texreg")
library("here")
library("tidyverse")
library("stringr")
library("broom.mixed")
library("kableExtra")
library("cowplot")

# set rstan options
rstan::rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores() )

# enables / disables caching for all chunks of code
knitr::opts_chunk$set(cache = TRUE)
```

```{r set-options_sm, echo = FALSE, cache = FALSE}
knitr::opts_chunk$set(fig.retina = 2.5)
options(width = 100)
```

\pagebreak

# Participants sample size

We conducted a separate study involving two groups: one of $n$ = 29 anorexic patients and one of $n$ = 124 healthy controls (the participants in that separate study were distinct from those in the present study). In a PRL task, each participant completed 160 trials per condition, and the content of the pair of images shown in each trial was manipulated. The effect size of the experimental manipulation on the learning rate parameter (the focus of the present study) was found to be 0.54. To determine the sample size needed to detect a similar effect, we carried out a parameter recovery study following the method outlined by @pedersen2020simultaneous. We simulated the data of two groups of 30 participants with different values of $\alpha$ (lower and higher) with a difference of 0.54. The other parameters of the RLDDM model (i.e., $a$, $t$, $v$) were set to the values estimated from the empirical data of the 29 anorexic patients and 124 healthy controls. For the simulation, we used the `hddm.generate.gen_rand_rlddm_data` function of the `hddm` module with following parameters:

```
subjects = 30
trials = 160

data = hddm.generate.gen_rand_rlddm_data(
    a=1.5,
    alpha=0.79, # or 0.25
    scaler=2.25,
    t=0.25,
    size=trials,
    subjs=subjects,
    p_upper=0.7,
    p_lower=0.3,
)
```

We used the `HDDMrl` function of the `hddm` module to estimate the RLDDM parameters based on the simulated data. We repeated this procedure 100 times, and in each iteration, the parameters for the lower and higher values of $\alpha$ were completely separated. These simulations indicate that our study had enough participants and trials to detect the effect size on $\alpha$ that had been observed in the previous study.

A parameter recovery study and a frequentist power analysis are two distinct approaches. However, since Bayesian methods prioritize estimation over hypothesis testing, it is comforting to see that with the current number of participants and trials, the RLDDM model can detect an effect size similar to the one found in a separate study with a different group of participants but with a similar experimental manipulation.

# Demographic and psychopathology measures

## Age

In our initial statistical analysis, we investigated if there were any differences in age among the groups (AN = Anorexia Nervosa, BN = Bulimia Nervosa, HC = Healthy Controls, RI = participants who were at risk of developing eating disorders but had not received a formal diagnosis).

The mean age and standard devitation by group is shown below.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
quest_param_df <- readr::read_csv(
  here::here("data", "processed", "quest", "quest.csv")
)

quest_param_df <- quest_param_df |> 
  dplyr::rename("group" = "diag_cat")

quest_param_df$group <- factor(quest_param_df$group)
quest_param_df$group <- relevel(quest_param_df$group, ref = "HC")
# contrasts(quest_param_df$group)
```

```{r, echo=FALSE}
quest_param_df |> 
  group_by(group) |> 
  summarize(
    Age = mean(age),
    SD = sd(age)
  ) |> 
   kable(digits = 2)
```

\vspace{5mm}

We used a Bayesian regression model to examine the age differences among groups.

```{r, message=FALSE, warning=FALSE, cache=TRUE}
m1 <- brm(
  age ~ group,
  data = quest_param_df,
  family = skew_normal(),
  iter = 4000,
  cores = parallel::detectCores(),
  backend = "cmdstan",
  refresh = 0,
  silent = TRUE
)
```

### Posterior predictive check

```{r, echo=FALSE}
pp_check(m1) +
  theme_cowplot()
```

\vspace{5mm}

### Model's coefficients

The estimations obtained for the model are summarized in Table below, which includes the mean, the standard error, and the lower and upper bounds of the 95% credible interval of the posterior distribution for each parameter. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
tidy(m1, effect="fixed", conf.method="HPDinterval", prob = 0.95) |>
  dplyr::select("term", "estimate", "std.error", "conf.low", "conf.high") |>
   kable(digits = 3)
```

\vspace{5mm}

The 95% credibility intervals for the difference in age between each group and the HC baseline included zero, indicating that there were no credible differences in age among the groups.

### Predicted effect of group on age

```{r, echo=FALSE}
c_eff <- conditional_effects(m1, "group")
plot(c_eff, plot = FALSE)[[1]] + 
  labs(
    y = "Age (years)",
    x = "Group") +
  theme_cowplot() + 
  coord_flip()
```

\pagebreak

## Body Mass Index (BMI)

\vspace{5mm}

The average Body Mass Index (BMI) values and standard deviations for each group are reported below.

```{r, message = FALSE, warning = FALSE, include = FALSE}
quest_param_df$bmi <- quest_param_df$present_weight / (quest_param_df$height/100)^2

quest_param_df[quest_param_df$group == "AN", ]$bmi |> sort()

ano <- quest_param_df[quest_param_df$group == "AN", ]
ano_df <- distinct(ano, subj_code, .keep_all = TRUE)
foo <- ano_df |> 
  dplyr::select(subj_code, height, present_weight, bmi)

foo |> as.data.frame()

quest_param_df$present_weight <- ifelse(
  quest_param_df$subj_code == "cr_pa_1969_04_12_179_f",
  40.2, quest_param_df$present_weight
) 

quest_param_df$present_weight <- ifelse(
  (quest_param_df$bmi > 19) & (quest_param_df$group == "AN"), 
  quest_param_df$present_weight - 10, quest_param_df$present_weight
)

quest_param_df$bmi <- quest_param_df$present_weight / (quest_param_df$height/100)^2

quest_param_df |> 
  group_by(group) |> 
  summarize(
    avg_bmi = mean(bmi),
    std_bmi = sd(bmi)
  )

bul <- quest_param_df[quest_param_df$group == "BN", ]
bul_df <- distinct(bul, subj_code, .keep_all = TRUE)
foo <- bul_df |> 
  dplyr::select(subj_code, height, present_weight, bmi)

quest_param_df$present_weight <- ifelse(
  quest_param_df$subj_code == "ga_gi_2003_02_09_229_f",
  82, quest_param_df$present_weight
) 

quest_param_df$present_weight <- ifelse(
  quest_param_df$subj_code == "ma_ba_1995_05_25_321_f",
  89, quest_param_df$present_weight
) 

quest_param_df$present_weight <- ifelse(
  quest_param_df$subj_code == "an_am_1996_05_12_176_f",
  79, quest_param_df$present_weight
)

quest_param_df$present_weight <- ifelse(
  quest_param_df$subj_code == "gr_de_2002_09_21_426_f",
  77, quest_param_df$present_weight
)

quest_param_df$present_weight <- ifelse(
  quest_param_df$subj_code == "gi_to_1996_02_02_043_f",
  82, quest_param_df$present_weight
) 

quest_param_df$bmi <- quest_param_df$present_weight / (quest_param_df$height/100)^2
```

\vspace{5mm}

```{r, echo=FALSE}
quest_param_df |> 
  group_by(group) |> 
  summarize(
    BMI = mean(bmi),
    SD = sd(bmi)
  ) |> 
   kable(digits = 2)
```

\vspace{5mm}

We used a Bayesian regression model to examine the BMI differences among groups.

\vspace{5mm}

```{r, message=FALSE, warning=FALSE, cache=TRUE}
m2 <- brm(
  bmi ~ group,
  data = quest_param_df, 
  family = skew_normal(),
  iter = 4000,
  cores = 4,
  backend = "cmdstan",
  refresh = 0,
  silent = TRUE
)
```

### Posterior predictive check

```{r, echo=FALSE}
pp_check(m2) +
  theme_cowplot()
```

\vspace{5mm}

### Model's coefficients

The estimations obtained for the model are summarized in Table below, which includes the mean, the standard error, and the lower and upper bounds of the 95% credible interval of the posterior distribution for each parameter. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
tidy(m2, effect="fixed", conf.method="HPDinterval", prob = 0.95) |>
  dplyr::select("term", "estimate", "std.error", "conf.low", "conf.high") |>
   kable(digits = 3)
```

\vspace{5mm}

The 95% credibility intervals for the difference in age between each group and the HC baseline do not include zero, indicating credible BMI differences between the AN and the HC groups, and between the BN and the HC groups. The at-risk and HC groups did not differ in terms of their average BMI values.

### Predicted effect of group on BMI

```{r, echo=FALSE}
c_eff <- conditional_effects(m2, "group")
plot(c_eff, plot = FALSE)[[1]] + 
  labs(
    y = "BMI",
    x = "Group")  +
  theme_cowplot() + 
  coord_flip()
```

\vspace{5mm}

## Rosenberg scale

\vspace{5mm}

The average score of the Rosenberg scale as a function of group is shown below.

```{r, echo=FALSE}
ros_df <- quest_param_df |> 
  dplyr::select(
    ros_tot, group, subj_code
  )
ros_df <- distinct(ros_df, subj_code, .keep_all = TRUE)

ros_df |> 
  group_by(group) |> 
  summarize(
    Rosenberg = mean(ros_tot),
    SD = sd(ros_tot)
  ) |> 
   kable(digits = 2)
```

\vspace{5mm}

We used a Bayesian regression model to examine the differences in Rosenberg self-esteem scores among groups.

```{r, message=FALSE, warning=FALSE, cache=TRUE}
m3 <- brm(
  ros_tot ~ group,
  data = ros_df,
  family = skew_normal(),
  iter = 4000,
  cores = parallel::detectCores(),
  backend = "cmdstan",
  refresh = 0,
  silent = TRUE
)
```

### Posterior predictive check

```{r, echo=FALSE}
pp_check(m3) +
  theme_cowplot() 
```

\vspace{5mm}

### Model's coefficients

The estimations obtained for the model are summarized in Table below, which includes the mean, the standard error, and the lower and upper bounds of the 95% credible interval of the posterior distribution for each parameter. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
tidy(m3, effect="fixed", conf.method="HPDinterval", prob = 0.95) |>
  dplyr::select("term", "estimate", "std.error", "conf.low", "conf.high") |>
   kable(digits = 3)
```

\vspace{5mm}

The 95% credibility intervals for the difference in the Rosenberg self-esteem scores between each group and the HC baseline do not include zero, indicating credible differences in the Rosenberg self-esteem scores between the HC and the other groups.

### Predicted effect of group on the Rosenberg self-esteem scores

```{r, echo=FALSE}
c_eff <- conditional_effects(m3, "group")
plot(c_eff, plot = FALSE)[[1]] + 
  labs(
    y = "Rosenberg self-esteem scale",
    x = "Group") +
  theme_cowplot() +
  coord_flip()
```

## Body Shape Questionnaire-14 (BSQ-14)

The average Body Shape Questionnaire-14 score as a function of group is shown below.

\vspace{5mm}

```{r, echo=FALSE}
bsq_df <- quest_param_df |> 
  dplyr::select(
    bsq14_tot, group, subj_code
  )
bsq_df <- distinct(bsq_df, subj_code, .keep_all = TRUE)

bsq_df$bsq14 <- bsq_df$bsq14_tot * 34/14

bsq_df |> 
  group_by(group) |> 
  summarize(
    BSQ_14 = mean(bsq14),
    SD = sd(bsq14)
  ) |> 
   kable(digits = 2)
```

\vspace{5mm}

We used a Bayesian regression model to examine the BSQ-14 differences among groups.

\vspace{5mm}

```{r, message=FALSE, warning=FALSE, cache=TRUE}
m4 <- brm(
  ros_tot ~ group,
  data = ros_df,
  family = skew_normal(),
  iter = 4000,
  cores = parallel::detectCores(),
  backend = "cmdstan",
  refresh = 0,
  silent = TRUE
)
```

### Posterior predictive check

```{r, echo=FALSE}
pp_check(m4) + 
  theme_cowplot()
```

\vspace{5mm}

### Model's coefficients

The estimations obtained for the model are summarized in Table below, which includes the mean, the standard error, and the lower and upper bounds of the 95% credible interval of the posterior distribution for each parameter. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
tidy(m4, effect="fixed", conf.method="HPDinterval", prob = 0.95) |>
  dplyr::select("term", "estimate", "std.error", "conf.low", "conf.high") |>
   kable(digits = 3)
```

\vspace{5mm}

The 95% credibility intervals for the difference in the BSQ-14 scores between each group and the HC baseline do not include zero, indicating credible differences in the BSQ-14 scores between the HC and the other groups.

### Predicted effect of group on the BSQ-14 scores

```{r, echo=FALSE}
c_eff <- conditional_effects(m4, "group")
plot(c_eff, plot = FALSE)[[1]] + 
  labs(
    y = "BSQ-14",
    x = "Group") + 
  theme_cowplot() +
  coord_flip() 
```

\pagebreak

## Depression Anxiety Stress Scale-21 (DASS-21)

```{r, echo=FALSE}
temp <- quest_param_df %>% 
  dplyr:: select(subj_code, group, starts_with("dass_"), "dass21_s", "dass21_a", 
                 "dass21_d")

dass_df <- distinct(temp, subj_code, .keep_all = TRUE)
```

Average values of the scores on the Stress, Anxiety, and Depression of the DASS-21 scale are shown below.

```{r, echo=FALSE}
dass_df |> 
  group_by(group) |> 
  summarize(
    Stress = mean(dass21_s),
    Anxiety = mean(dass21_a),
    Depression = mean(dass21_d)
  ) |> 
   kable(digits = 2)
```

Standard deviations of the scores on the Stress, Anxiety, and Depression sub-scales are shown below.

\vspace{5mm}

```{r, echo=FALSE}
dass_df |> 
  group_by(group) |> 
  summarize(
    SD_stress = mean(dass21_s),
    SD_anxiety = mean(dass21_a),
    SD_depression = mean(dass21_d)
  ) |> 
   kable(digits = 2)
```

\vspace{5mm}

### Stress

We used a Bayesian regression model to examine the DASS-21 Stress differences among groups.

```{r, message=FALSE, warning=FALSE, cache=TRUE}
m5_s <- brm(
  dass21_s ~ group,
  data = dass_df, 
  family = gaussian(),
  iter = 4000,
  cores = 4,
  backend = "cmdstan",
  refresh = 0,
  silent = TRUE
)
```

### Posterior predictive check

```{r, echo=FALSE}
pp_check(m5_s) +
  theme_cowplot()
```

\vspace{5mm}

### Model's coefficients

The estimations obtained for the model are summarized in Table below, which includes the mean, the standard error, and the lower and upper bounds of the 95% credible interval of the posterior distribution for each parameter. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
tidy(m5_s, effect="fixed", conf.method="HPDinterval", prob = 0.95) |>
  dplyr::select("term", "estimate", "std.error", "conf.low", "conf.high") |>
   kable(digits = 3)
```

\vspace{5mm}

The 95% credibility intervals for the difference in the DASS-21 Stress scores between the AN and RI groups, on the one side, and the HC baseline, on the other, do not include zero, indicating credible differences in the DASS-21 Stress between the HC and the other two groups. We found no credible difference in the average DASS-21 Stress score between the HC and BC groups.

### Predicted effect of group on the DASS-21 Stress scores

```{r, echo=FALSE}
c_eff <- conditional_effects(m5_s, "group")
plot(c_eff, plot = FALSE)[[1]] + 
  labs(
    y = "DASS-21 Stress",
    x = "Group") + 
  theme_cowplot() +
  coord_flip()
```

### Anxiety

We used a Bayesian regression model to examine the DASS-21 Anxiety differences among groups.

```{r, message=FALSE, warning=FALSE, cache=TRUE}
m5_a <- brm(
  dass21_a ~ group,
  data = dass_df, 
  family = skew_normal(),
  iter = 4000,
  cores = 4,
  backend = "cmdstan",
  refresh = 0,
  silent = TRUE
)
```

### Posterior predictive check

```{r, echo=FALSE}
pp_check(m5_a) + 
  theme_cowplot() 
```

\vspace{5mm}

### Model's coefficients

The estimations obtained for the model are summarized in Table below, which includes the mean, the standard error, and the lower and upper bounds of the 95% credible interval of the posterior distribution for each parameter. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
tidy(m5_a, effect="fixed", conf.method="HPDinterval", prob = 0.95) |>
  dplyr::select("term", "estimate", "std.error", "conf.low", "conf.high") |>
   kable(digits = 3)
```

\vspace{5mm}

The 95% credibility intervals for the difference in the DASS-21 Anxiety scores between the AN and the HC baseline do not include zero, indicating credible differences in the DASS-21 Anxiety between the two groups. We found no credible difference in the average DASS-21 Anxiety score between the HC and BC groups, nor between the HC and the RI groups.

### Predicted effect of group on the DASS-21 Anxiety scores

```{r, echo=FALSE}
c_eff <- conditional_effects(m5_a, "group")
plot(c_eff, plot = FALSE)[[1]] + 
  labs(
    y = "DASS-21 Anxiety",
    x = "Group") + 
  theme_cowplot() +
  coord_flip()
```

### Depression

We used a Bayesian regression model to examine the DASS-21 Depression differences among groups.

```{r, message=FALSE, warning=FALSE, cache=TRUE}
m5_d <- brm(
  dass21_d ~ group,
  data = dass_df, 
  family = skew_normal(),
  iter = 4000,
  cores = 4,
  backend = "cmdstan",
  refresh = 0,
  silent = TRUE
)
```

### Posterior predictive check

```{r, echo=FALSE}
pp_check(m5_d) + 
  theme_cowplot()
```

\vspace{5mm}

### Model's coefficients

The estimations obtained for the model are summarized in Table below, which includes the mean, the standard error, and the lower and upper bounds of the 95% credible interval of the posterior distribution for each parameter. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
tidy(m5_d, effect="fixed", conf.method="HPDinterval", prob = 0.95) |>
  dplyr::select("term", "estimate", "std.error", "conf.low", "conf.high") |>
   kable(digits = 3)
```

\vspace{5mm}

The 95% credibility intervals for the difference in the DASS-21 Depression scores between the AN, BN, and RI groups, on the one side, and the HC baseline, on the other, do not include zero, indicating credible differences in the DASS-21 Anxiety between the baseline group and the other groups. 

### Predicted effect of group on the DASS-21 Depression scores

```{r, echo=FALSE}
c_eff <- conditional_effects(m5_d, "group")
plot(c_eff, plot = FALSE)[[1]] + 
  labs(
    y = "DASS-21 Depression",
    x = "Group") + 
  theme_cowplot() +
  coord_flip()
```

\pagebreak

## Social Interaction Anxiety Scale (SIAS)

```{r, echo=FALSE}
temp <- quest_param_df %>% 
  dplyr:: select(subj_code, group, starts_with("sias_"))

sias_df <- distinct(temp, subj_code, .keep_all = TRUE)
```

```{r, echo=FALSE}
sias_df |> 
  group_by(group) |> 
  summarize(
    SIAS = mean(sias_tot),
    SD = sd(sias_tot)
  ) |> 
   kable(digits = 2)
```

\vspace{5mm}

We used a Bayesian regression model to examine the SIAS score differences among groups.

\vspace{5mm}

```{r, message=FALSE, warning=FALSE, cache=TRUE}
m6 <- brm(
  sias_tot ~ group,
  data = sias_df,
  family = skew_normal(),
  iter = 4000,
  cores = parallel::detectCores(),
  backend = "cmdstan",
  refresh = 0,
  silent = TRUE
)
```

### Posterior predictive check

```{r, echo=FALSE}
pp_check(m6) + 
  theme_cowplot()
```

\vspace{5mm}

### Model's coefficients

The estimations obtained for the model are summarized in Table below, which includes the mean, the standard error, and the lower and upper bounds of the 95% credible interval of the posterior distribution for each parameter. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
tidy(m6, effect="fixed", conf.method="HPDinterval", prob = 0.95) |>
  dplyr::select("term", "estimate", "std.error", "conf.low", "conf.high") |>
   kable(digits = 3)
```

\vspace{5mm}

The 95% credibility intervals for the difference in the SIAS scores between the AN and RI groups, on the one side, and the HC baseline, on the other do not include zero, indicating credible differences in the SIAS scores between the HC and these two groups. We found no credible difference in the average SIAS scores between the BN and the HC groups.

### Predicted effect of group on the SIAS scores

```{r, echo=FALSE}
c_eff <- conditional_effects(m6, "group")
plot(c_eff, plot = FALSE)[[1]] + 
  labs(
    y = "SIAS",
    x = "Group") + 
  theme_cowplot() +
  coord_flip()
```

\pagebreak

## Multidimensional Perfectionism Scale (MPS)

The average scores on the sub-scales of Concerns over Mistakes and Doubts (CMD), Parental Expectations and Criticism (PEC), Personal Standards (PS), and Organization (O) of the MPS as a function of group are shown below.

```{r, echo=FALSE}
temp <- quest_param_df %>% 
  dplyr:: select(subj_code, group, starts_with("mps_"))

mps_df <- distinct(temp, subj_code, .keep_all = TRUE)

mps_df |> 
  group_by(group) |> 
  summarize(
    MPS_cmd = mean(mps_cmd),
    MPS_ps = mean(mps_ps),
    MPS_pepc = mean(mps_pepc),
    MPS_or = mean(mps_or)
  ) |> 
   kable(digits = 2)
```

The standard deviations on the sub-scales of Concerns over Mistakes and Doubts (CMD), Parental Expectations and Criticism (PEC), Personal Standards (PS), and Organization (O) of the MPS as a function of group are shown below.

```{r, echo=FALSE}
mps_df |> 
  group_by(group) |> 
  summarize(
    SD_cmd = sd(mps_cmd),
    SD_ps = sd(mps_ps),
    SD_pepc = sd(mps_pepc),
    SD_or = sd(mps_or)
  ) |> 
   kable(digits = 2)
```

### Concerns over Mistakes and Doubts

We used a Bayesian regression model to examine the MPS CMD score differences among groups.

\vspace{5mm}

```{r, message=FALSE, warning=FALSE, cache=TRUE}
m7_cmd <- brm(
  mps_cmd ~ group,
  data = mps_df,
  family = gaussian(),
  iter = 4000,
  cores = parallel::detectCores(),
  backend = "cmdstan",
  refresh = 0,
  silent = TRUE
)
```

### Posterior predictive check

```{r, echo=FALSE}
pp_check(m7_cmd) + 
  theme_cowplot()
```

\vspace{5mm}

### Model's coefficients

The estimations obtained for the model are summarized in Table below, which includes the mean, the standard error, and the lower and upper bounds of the 95% credible interval of the posterior distribution for each parameter. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
tidy(m7_cmd, effect="fixed", conf.method="HPDinterval", prob = 0.95) |>
  dplyr::select("term", "estimate", "std.error", "conf.low", "conf.high") |>
   kable(digits = 3)
```

\vspace{5mm}

The 95% credibility intervals for the difference in the SIAS scores between the HC and the other groups do not include zero, indicating credible differences in the MPS-CMD  scores between the HC and the other groups.

### Predicted effect of group on the MPS Concerns over Mistakes and Doubts

```{r, echo=FALSE}
c_eff <- conditional_effects(m7_cmd, "group")
plot(c_eff, plot = FALSE)[[1]] + 
  labs(
    y = "MPS Concerns over Mistakes and Doubts",
    x = "Group") + 
  theme_cowplot() +
  coord_flip()
```

### Parental Expectations and Criticism

We used a Bayesian regression model to examine the MPS PEC score differences among groups.

\vspace{5mm}

```{r, message=FALSE, warning=FALSE, cache=TRUE}
m7_pec <- brm(
  mps_pepc ~ group,
  data = mps_df,
  family = skew_normal(),
  iter = 4000,
  cores = parallel::detectCores(),
  backend = "cmdstan",
  refresh = 0,
  silent = TRUE
)
```

### Posterior predictive check

```{r, echo=FALSE}
pp_check(m7_pec) + 
  theme_cowplot()
```

\vspace{5mm}

### Model's coefficients

The estimations obtained for the model are summarized in Table below, which includes the mean, the standard error, and the lower and upper bounds of the 95% credible interval of the posterior distribution for each parameter. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
tidy(m7_pec, effect="fixed", conf.method="HPDinterval", prob = 0.95) |>
  dplyr::select("term", "estimate", "std.error", "conf.low", "conf.high") |>
   kable(digits = 3)
```

\vspace{5mm}

The 95% credibility intervals for the difference in the MPS-PEC scores between the HC and the RI group do not include zero, indicating credible differences in Parental Expectations and Criticism between these two groups. We found no credible difference in MPS-PEC between the HC group, on the one side, and the AN and BN groups, on the other.

### Predicted effect of group on the MPS Parental Expectations and Criticism

```{r, echo=FALSE}
c_eff <- conditional_effects(m7_pec, "group")
plot(c_eff, plot = FALSE)[[1]] + 
  labs(
    y = "MPS Parental Expectations and Criticism",
    x = "Group") + 
  theme_cowplot() +
  coord_flip()
```

### Personal Standards

We used a Bayesian regression model to examine the MPS PS score differences among groups.

\vspace{5mm}

```{r, message=FALSE, warning=FALSE, cache=TRUE}
m7_ps <- brm(
  mps_ps ~ group,
  data = mps_df,
  family = gaussian(),
  iter = 4000,
  cores = parallel::detectCores(),
  backend = "cmdstan",
  refresh = 0,
  silent = TRUE
)
```

### Posterior predictive check

```{r, echo=FALSE}
pp_check(m7_ps) + 
  theme_cowplot()
```

\vspace{5mm}

### Model's coefficients

The estimations obtained for the model are summarized in Table below, which includes the mean, the standard error, and the lower and upper bounds of the 95% credible interval of the posterior distribution for each parameter. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
tidy(m7_ps, effect="fixed", conf.method="HPDinterval", prob = 0.95) |>
  dplyr::select("term", "estimate", "std.error", "conf.low", "conf.high") |>
   kable(digits = 3)
```

\vspace{5mm}

The 95% credibility intervals for the difference in the MPS-PS scores between the HC group, on the one side, and the AN and RI groups, on the other, do not include zero, indicating credible differences in Personal standards between these groups. We found no credible difference in MPS-PS between the HC group and the BN groups.

### Predicted effect of group on the MPS Personal Standards scores

```{r, echo=FALSE}
c_eff <- conditional_effects(m7_ps, "group")
plot(c_eff, plot = FALSE)[[1]] + 
  labs(
    y = "MPS Personal Standards",
    x = "Group") + 
  theme_cowplot() +
  coord_flip()
```

### Organization

We used a Bayesian regression model to examine the MPS-O score differences among groups.

\vspace{5mm}

```{r, message=FALSE, warning=FALSE, cache=TRUE}
m7_or <- brm(
  mps_or ~ group,
  data = mps_df,
  family = skew_normal(),
  iter = 4000,
  cores = parallel::detectCores(),
  backend = "cmdstan",
  refresh = 0,
  silent = TRUE
)
```

### Posterior predictive check

```{r, echo=FALSE}
pp_check(m7_or) + 
  theme_cowplot()
```

\vspace{5mm}

### Model's coefficients

The estimations obtained for the model are summarized in Table below, which includes the mean, the standard error, and the lower and upper bounds of the 95% credible interval of the posterior distribution for each parameter. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
tidy(m7_or, effect="fixed", conf.method="HPDinterval", prob = 0.95) |>
  dplyr::select("term", "estimate", "std.error", "conf.low", "conf.high") |>
   kable(digits = 3)
```

\vspace{5mm}

The 95% credibility intervals for the difference in the MPS-O scores between the HC group, on the one side, and the AN, BN, and RI groups, on the other, do include zero, indicating that there are no credible differences in Organization between these groups.

### Predicted effect of group on the MPS Organization scores

```{r, echo=FALSE}
c_eff <- conditional_effects(m7_or, "group")
plot(c_eff, plot = FALSE)[[1]] + 
  labs(
    y = "MPS Organization",
    x = "Group") + 
  theme_cowplot() +
  coord_flip()
```

\pagebreak

## Eating Attitude Test-26 (EAT-26)

The average scores on the Dieting Scale, the Bulimia and Food Preoccupation Scale, and the Oral Control Scale as a function of group are shown below. The average scores of each sub-scale and of the EAT-26 total score, as a function of group, are show below together with the standard deviations.

```{r, echo=FALSE}
temp <- quest_param_df %>% 
  dplyr:: select(subj_code, group, starts_with("eat26_"))

eat26_df <- distinct(temp, subj_code, .keep_all = TRUE)

eat26_df$dieting <- with(
  eat26_df,
  eat26_1 + eat26_6 + eat26_7 + eat26_10 + eat26_11 + eat26_12 + eat26_14 + 
  eat26_16 + eat26_17 + eat26_22 + eat26_23 + eat26_24 + eat26_26
)

eat26_df$bulimia <- with(
  eat26_df,
  eat26_3 + eat26_4 + eat26_9 + eat26_18 + eat26_21 + eat26_25
)

eat26_df$oral_control <- with(
  eat26_df,
  eat26_2 + eat26_5 + eat26_8 + eat26_13 + eat26_15 + eat26_19 + eat26_20
)

eat26_df$eat26tot <- with(
  eat26_df,
  eat26_1 + eat26_6 + eat26_7 + eat26_10 + eat26_11 + eat26_12 + eat26_14 + 
  eat26_16 + eat26_17 + eat26_22 + eat26_23 + eat26_24 + eat26_26 +
    eat26_3 + eat26_4 + eat26_9 + eat26_18 + eat26_21 + eat26_25 +
    eat26_2 + eat26_5 + eat26_8 + eat26_13 + eat26_15 + eat26_19 + eat26_20
)

eat26_df |> 
  group_by(group) |> 
  summarize(
    EAT26_dieting = mean(dieting),
    EAT26_bulimia = mean(bulimia),
    EAT26_oralcontrol = mean(oral_control),
    EAT26_tot = mean(eat26tot)
  ) |> 
   kable(digits = 2)
```

```{r, echo=FALSE}
eat26_df |> 
  group_by(group) |> 
  summarize(
    SD_dieting = sd(dieting),
    SD_bulimia = sd(bulimia),
    SD_oralcontrol = sd(oral_control),
    SD_tot = sd(eat26tot)
  ) |> 
   kable(digits = 2)
```

### Dieting

We used a Bayesian regression model to examine the EAT-26 Dieting score differences among groups.

\vspace{5mm}

```{r, message=FALSE, warning=FALSE, cache=TRUE}
m8_d <- brm(
  dieting ~ group,
  data = eat26_df,
  family = hurdle_lognormal(),
  iter = 4000,
  cores = parallel::detectCores(),
  backend = "cmdstan",
  refresh = 0,
  silent = TRUE
)
```
### Posterior predictive check

```{r, echo=FALSE}
pp_check(m8_d) + xlim(0, 75) + 
  theme_cowplot()
```

\vspace{5mm}

### Model's coefficients

The estimations obtained for the model are summarized in Table below, which includes the mean, the standard error, and the lower and upper bounds of the 95% credible interval of the posterior distribution for each parameter. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
tidy(m8_d, effect="fixed", conf.method="HPDinterval", prob = 0.95) |>
  dplyr::select("term", "estimate", "std.error", "conf.low", "conf.high") |>
   kable(digits = 3)
```

\vspace{5mm}

The 95% credibility intervals for the difference in the EAT-26 Dieting scores between the HC group, on the one side, and the AN, BN, and RI groups, on the other, do not include zero, indicating a credible elevation in the EAT-26 Dieting scores of the AN, BN, and RI groups with respect to the HC group.

### Predicted effect of group on the EAT-26 Dieting scores

```{r, echo=FALSE}
c_eff <- conditional_effects(m8_d, "group")
plot(c_eff, plot = FALSE)[[1]] + 
  labs(
    y = "EAT-26 Dieting",
    x = "Group") + 
  theme_cowplot() +
  coord_flip()
```

### Bulimia and Food Preoccupation 

We used a Bayesian regression model to examine the EAT-26 Bulimia and Food Preoccupation score differences among groups.

\vspace{5mm}

```{r, message=FALSE, warning=FALSE, cache=TRUE}
m8_b <- brm(
  bulimia ~ group,
  data = eat26_df,
  family = hurdle_lognormal(),
  iter = 4000,
  cores = parallel::detectCores(),
  backend = "cmdstan",
  refresh = 0,
  silent = TRUE
)
```

### Posterior predictive check

```{r, echo=FALSE}
pp_check(m8_b) + xlim(0, 20) + 
  theme_cowplot()
```

\vspace{5mm}

### Model's coefficients

The estimations obtained for the model are summarized in Table below, which includes the mean, the standard error, and the lower and upper bounds of the 95% credible interval of the posterior distribution for each parameter. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
tidy(m8_b, effect="fixed", conf.method="HPDinterval", prob = 0.95) |>
  dplyr::select("term", "estimate", "std.error", "conf.low", "conf.high") |>
   kable(digits = 3)
```

\vspace{5mm}

The 95% credibility intervals for the difference in the EAT-26 Bulimia and Food Preoccupation scores between the HC group, on the one side, and the AN, BN, and RI groups, on the other, do not include zero, indicating a credible elevation in the EAT-26 Bulimia and Food Preoccupation scores of the clinical and at-risk groups with respect to the HC group.

### Predicted effect of group on the EAT-26 Dieting scores

```{r, echo=FALSE}
c_eff <- conditional_effects(m8_b, "group")
plot(c_eff, plot = FALSE)[[1]] + 
  labs(
    y = "EAT-26 Dieting",
    x = "Group") + 
  theme_cowplot() +
  coord_flip()
```


### Oral Control 

We used a Bayesian regression model to examine the EAT-26 Oral Control score differences among groups.

\vspace{5mm}

```{r, message=FALSE, warning=FALSE, cache=TRUE}
m8_oc <- brm(
  oral_control ~ group,
  data = eat26_df,
  family = hurdle_lognormal(),
  iter = 4000,
  cores = parallel::detectCores(),
  backend = "cmdstan",
  refresh = 0,
  silent = TRUE
)
```
### Posterior predictive check

```{r, echo=FALSE}
pp_check(m8_oc) + xlim(0, 20) + 
  theme_cowplot()
```

\vspace{5mm}

### Model's coefficients

The estimations obtained for the model are summarized in Table below, which includes the mean, the standard error, and the lower and upper bounds of the 95% credible interval of the posterior distribution for each parameter. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
tidy(m8_oc, effect="fixed", conf.method="HPDinterval", prob = 0.95) |>
  dplyr::select("term", "estimate", "std.error", "conf.low", "conf.high") |>
   kable(digits = 3)
```

\vspace{5mm}

The 95% credibility intervals for the difference in the EAT-26 Oral Control scores between the HC group, on the one side, and the AN, BN, and RI groups, on the other, do not include zero, indicating a credible elevation in the EAT-26 Oral Control scores of the clinical and at-risk groups with respect to the HC group.

### Predicted effect of group on the EAT-26 Oral Control

```{r, echo=FALSE}
c_eff <- conditional_effects(m8_oc, "group")
plot(c_eff, plot = FALSE)[[1]] + 
  labs(
    y = "EAT-26 Oral Control",
    x = "Group") + 
  theme_cowplot() +
  coord_flip()
```

\pagebreak

## Participants Sample Size

\pagebreak



## Outcome-irrelevant learning: spatial-motor associations

In order to investigate whether the likelihood of selecting 'stay' was greater for 'same' versus 'flipped' response/key mapping, when contrasting rewarded and unrewarded responses, we reproduced the statistical evaluations conducted by @shahar2019credit and @ben2022working. First, we employed a 3-way interaction model that permitted the modulation of the interaction between 'same/flipped' response/key mapping $\times$ previously rewarded/unrewarded responses to vary across different groups. 

```{r setup2, message = FALSE, warning = FALSE, include = FALSE, results = "hide", cache=TRUE}

# Prelims
suppressPackageStartupMessages({
  library("here")
  library("tidyverse")
  library("stringi")
  library("readxl")
  library("brms")
  library("marginaleffects")
  library("insight")
  library("see")
  library("bayestestR")
})

# Increase max print
options(max.print = .Machine$integer.max)

source(here::here("src", "R", "functions", "funs_prl.R"))
source(here::here("src", "R", "functions", "funs_consecutive_trial_analysis.R"))

# get subj_codes of the final set of 296 subjects.
source(here::here("data", "processed", "prl", "subj_codes_296.R"))

# Read list of subjects used in the hDDMrl analysis.
lookup_tbl <- rio::import(
  here::here(
    "data", "processed", "prl", "input_for_hddmrl", 
    "hddm_look_up_table_v3.csv"
  )
)

# Read complete raw data.
d1 <- gen_data_for_consecutive_trial_analysis()

# Select only 296 subjects.

d2 <- d1[d1$subj_name %in% subj_codes_296, ]
length(unique(d2$subj_name))
# [1] 296

d <- d2 |>
  dplyr::rename(
    subj_code = subj_name
  )

length(unique(d$subj_code))
summary(factor(d$diag_cat))
setdiff(unique(d$subj_code), unique(lookup_tbl$subj_code))

# Recode feedback
table(d$feedback)
#     0     1 
# 39636 47244 

d$diag_cat <- recode_factor(
  d$diag_cat,
  "AN_R" = "RI",
  "BN_R" = "RI"
)

d |> 
  group_by(diag_cat) |> 
  summarize(
    n_distinct(subj_code)
  )
# 1 RI                            35
# 2 AN                            37
# 3 BN                            12
# 4 HC                           212


# Add lead variables ------------------------------------------------------

# Test.
# foo <- tibble(
#   idx = rep(c("a", "b"), each = 10),
#   blk = rep(1:4, each = 5),
#   x = c(1:5, 1:5, 1:5, 1:5)
# )
# 
# foo <- foo |>
#   group_by(idx, blk) |>
#   mutate(
#     x_lag = lag(x)
#   )


# Is mapping same ---------------------------------------------------------

# Same mapping:
# 1 (same): target position in i trial == target position in i-1 trial
# 0 (different): target position in i trial != target position in i-1 trial

# prev_position_target_img
d <- d |>
  group_by(subj_code, stimulus_type) |> 
  mutate(
    prev_position_target_img = lag(position_target_img)
)
# foo <- tibble(
#   position_target_img = df$position_target_img,  
#   prev_position_target_img = df$prev_position_target_img
# )

d <- d |> 
  group_by(subj_code, stimulus_type) |> 
  mutate(
    is_mapping_same = ifelse(
      position_target_img == prev_position_target_img, 1, 0
    )
  )
# table(df$is_mapping_same)
# foo <- tibble(
#   position_target_img = df$position_target_img,
#   prev_position_target_img = df$prev_position_target_img,
#   is_mapping_same = df$is_mapping_same
# )


# Stay (image) ------------------------------------------------------------

# Which image has been chosen?
# In epoch 1, let's call A the target image.
# If is_target_rewarded_in_present_epoch == 1 and is_target_img_chosen == 1,
# then participant has chosen the image A.
# If is_target_rewarded_in_present_epoch == 0 and is_target_img_chosen == 1,
# then participant has chosen the image B.

d <- d |> 
  group_by(subj_code) |> 
  mutate(
    is_img_a_chosen = case_when(
      is_target_rewared_in_present_epoch == 1 & is_target_img_chosen == 1 ~ "A",
      is_target_rewared_in_present_epoch == 0 & is_target_img_chosen == 1 ~ "B",
      is_target_rewared_in_present_epoch == 1 & is_target_img_chosen == 0 ~ "B",
      is_target_rewared_in_present_epoch == 0 & is_target_img_chosen == 0 ~ "A",
      TRUE ~ NA_character_
    )
  )
# summary(factor(d1$is_img_a_chosen))

# previous image chosen
d <- d |> 
  group_by(subj_code, stimulus_type) |> 
  mutate(
    prev_is_img_a_chosen = lag(is_img_a_chosen)
  )

# prev_feedback
d <- d |>
  group_by(subj_code, stimulus_type) |> 
  mutate(
    prev_feedback = lag(feedback)
  )
# foo <- tibble(
#   feedback = df$feedback,
#   prev_feedback = df$prev_feedback
# )

# Define stay
d <- d |>
  group_by(subj_code, diag_cat, stimulus_type, prev_feedback) |> 
  mutate(
    stay = ifelse(
      is_img_a_chosen == prev_is_img_a_chosen, 1, 0
    )
  )

# Mean stay
bysubj_df <- d |> 
  group_by(
    subj_code, diag_cat, stimulus_type, prev_feedback, is_mapping_same
    ) |> 
  summarize(
    stay = mean(stay, na.rm = TRUE),
    n = n()
  ) |> 
  ungroup()

bysubj_df <- bysubj_df[!is.na(bysubj_df$is_mapping_same), ]

# bysubj_df |> 
#   group_by(diag_cat, stimulus_type, prev_feedback, is_mapping_same) |> 
#   summarize(
#     stay = mean(stay, na.rm = TRUE),
#     n = n()
#   ) |> 
#   as.data.frame()

# There is no difference in the interaction is_mapping_same x prev_feedback as
# a function of stimulus_type, for the ED patients. So, I collapse the 'food'
# and 'neutral' conditions.

# I consider only the HC, AN, and BN groups.
bysubj_ed <- bysubj_df[bysubj_df$diag_cat %in% c("AN", "HC", "BN", "RI"), ]

# bysubj_ed$diag_cat <- ifelse(bysubj_ed$diag_cat == "HC", "HC", "ED")
# bysubj_ed$diag_cat <- factor(bysubj_ed$diag_cat)
# summary(bysubj_ed$diag_cat)

# all 4 categories
bysubj_ed <- bysubj_df

bysubj_ed %>%
  group_by(is_mapping_same, prev_feedback) %>%
  summarise(
    m = mean(stay)
  )
#   is_mapping_same prev_feedback     m
# 1               0             0 0.472
# 2               0             1 0.690
# 3               1             0 0.370
# 4               1             1 0.797

0.690 - 0.472
# [1] 0.218
0.797 - 0.370
# [1] 0.427

# Rename and recode variables.
bysubj_ed <- bysubj_ed |> 
  dplyr::rename(
    feedback = prev_feedback,
    mapping = is_mapping_same,
    image = stimulus_type,
    diagnosis = diag_cat)

bysubj_ed$feedback <- factor(bysubj_ed$feedback)
bysubj_ed$feedback <- bysubj_ed$feedback |> 
  forcats::fct_recode(
    "punishment" = "0",
    "reward" = "1"
  )

bysubj_ed$mapping <- factor(bysubj_ed$mapping)
bysubj_ed$mapping <- bysubj_ed$mapping |> 
  forcats::fct_recode(
    "flipped" = "0",
    "same" = "1"
  )

bysubj_ed$image <- factor(bysubj_ed$image)
bysubj_ed$diagnosis <- factor(bysubj_ed$diagnosis)
bysubj_ed$diagnosis <- relevel(bysubj_ed$diagnosis, ref = "HC")
contrasts(bysubj_ed$diagnosis)

summary(bysubj_ed$diagnosis)

bcpriors <- get_prior(
  stay ~ 0 + Intercept + mapping * feedback * diagnosis +
    (1 + mapping * feedback | subj_code),
  family = zero_one_inflated_beta(),
  data = bysubj_ed
)
```

**Three-way interaction**

```{r, message=FALSE, warning=FALSE, cache=TRUE}
priors_0 <- c(
  set_prior("student_t(3, 0, 0.2)", class = "b", coef = "Intercept"),
  set_prior("student_t(3, 0, 0.2)", class = "b"),
  set_prior("student_t(3, 0, 0.2)", class = "sd"),
  set_prior("lkj(1)", class = "cor"),
  set_prior("gamma(0.01, 0.01)", class = "phi"),
  set_prior("beta(2, 2)", class = "coi"),
  set_prior("beta(2, 2)", class = "zoi")
)

mod_0 <- brm(
  stay ~ 0 + Intercept + mapping * feedback * diagnosis + 
    (1 + mapping * feedback | subj_code),
  family = zero_one_inflated_beta(),
  backend = "cmdstanr",
  data = bysubj_ed,
  prior = priors_0,
  iter = 2000,
  refresh = 0,
  silent = TRUE
)
mod_0 <- add_criterion(mod_0, "loo")
```

### Posterior predictive check

```{r, echo=FALSE, cache=TRUE}
pp_check(mod_0) + 
  theme_cowplot()
```

\vspace{5mm}

### Model's coefficients

The estimations obtained for the model are summarized in Table below, which includes the mean, the standard error, and the lower and upper bounds of the 95% credible interval of the posterior distribution for each parameter. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
tidy(mod_0, effect="fixed", conf.method="HPDinterval", prob = 0.95) |>
  dplyr::select("term", "estimate", "std.error", "conf.low", "conf.high") |>
   kable(digits = 3)
```

\vspace{5mm}

```{r, echo=FALSE}
dcat <- make_conditions(mod_0, "diagnosis")
me <- conditional_effects(mod_0, "mapping:feedback", conditions = dcat)
plot(me, plot = FALSE)[[1]] +
  see::scale_colour_okabeito(order = c(1, 5)) +
  labs(
    x = "Mapping",
    y = "Stay"
  ) +
  papaja::theme_apa() +
  theme(legend.position="bottom") 
```

This model failed to yield convincing evidence of a 3-way interaction, prompting us to simplify it by disregarding variations across groups. 

```{r, message=FALSE, warning=FALSE, cache=TRUE}
bcpriors <- get_prior(
  stay ~ 0 + Intercept + mapping * feedback +
    (1 + mapping * feedback | subj_code),
  family = zero_one_inflated_beta(),
  data = bysubj_ed
)

priors_1 <- c(
  set_prior("student_t(3, 0, 0.2)", class = "b", coef = "Intercept"),
  set_prior("student_t(3, 0, 0.2)", class = "b"),
  set_prior("student_t(3, 0, 0.2)", class = "sd"),
  set_prior("lkj(1)", class = "cor"),
  set_prior("gamma(0.01, 0.01)", class = "phi"),
  set_prior("beta(2, 2)", class = "coi"),
  set_prior("beta(2, 2)", class = "zoi")
)

mod_1 <- brm(
  stay ~ 0 + Intercept + mapping * feedback +
    (1 + mapping * feedback | subj_code),
  family = zero_one_inflated_beta(),
  backend = "cmdstanr",
  data = bysubj_ed,
  prior = priors_1,
  iter = 2000,
  refresh = 0,
  silent = TRUE,
  save_pars = save_pars(all = TRUE)
)
mod_1 <- add_criterion(mod_1, "loo")
```

### Posterior predictive check

```{r, echo=FALSE, cache=TRUE}
pp_check(mod_1) + 
  theme_cowplot()
```

\vspace{5mm}

### Model's coefficients

The estimations obtained for the model are summarized in Table below, which includes the mean, the standard error, and the lower and upper bounds of the 95% credible interval of the posterior distribution for each parameter. 

\vspace{5mm}

```{r, message=FALSE, warning=FALSE, echo=FALSE}
tidy(mod_1, effect="fixed", conf.method="HPDinterval", prob = 0.95) |>
  dplyr::select("term", "estimate", "std.error", "conf.low", "conf.high") |>
   kable(digits = 3)
```

\vspace{5mm}

The following figure, which describes the predicted marginal effects, replicates Fig. 2C of Shahar et al. (2019).

\vspace{5mm}

```{r, echo=FALSE}
me <- conditional_effects(mod_1, "mapping:feedback")
plot(me, plot = FALSE)[[1]] +
  see::scale_colour_okabeito(order = c(1, 5)) +
  labs(
    x = "Mapping",
    y = "Stay"
  ) +
  papaja::theme_apa() +
  theme(legend.position="bottom") 
```

\pagebreak

## Data Analysis of the Probabilistic Reversal Learning Task

Tasks were programmed in MATLAB (MathWorks) using Psychtoolbox extensions (Brainard, 1997). Task structure is detailed in the main text methods. For all tasks, trials were interleaved by an inter-trial interval (ITI) drawn from a uniform distribution ITI  uniform (0.7s, 1s). During the ITI a fixation cross was displayed (.65o visual angle) to draw attention to the center of the screen. Next, stimuli were displayed on screen until a response was made or until a time deadline (3 seconds, learnt by the participant during practice trials) was reached. Overall, only 583 trials were lost due to time-outs (~0.58% of the total database). TODO

## Decision Process (RLDDM)

We utilized a reinforcement learning drift diffusion model [RLDDM; @pedersen2020simultaneous] to investigate the impact of illness-related information, which was irrelevant to the outcome, on decision-making. The RLDDM consists of two key components: one describes how reward feedback is employed to update value expectations and the other describes how an agent uses these expectations to arrive at a decision. The first component characterizes the learning process in terms of the delta learning rule [@rescorla1972theory]: 

$$
Q_{a, i} = Q_{a, i-1} + \alpha (I_{a, i-1} - Q_{a, i-1}).
$$

Here, $Q$ refers to the expected values for option $a$ on trial $i$, $I$ represents the reward (with values 1 or 0), and $\alpha$ is the leaning rate, which scales the difference between the expected and actual rewards.

The second component describes the selection rule for reinforced options. Typically, a softmax function is used, where the probability of selecting option $a$ depends on its expected value relative to other options $n$, scaled by the inverse temperature parameter $\beta$:

$$
p_{a,i} = \frac{e^{\beta Q_{a,i}}}{\sum_{j=1}^n e^{\beta Q_{j,i}}}.
$$

In the RLDDM, instead, this second component of decision-making is replaced by a Drift-Diffusion Model [DDM; @ratcliff2008diffusion] which assumes a stochastic accumulation of evidence on each trial. A drift rate parameter ($v$) describes the rate of (noisy) evidence accumulation; a decision threshold parameter ($a$) represents the amount of evidence needed to make a decision; a non-decision time parameter ($t$) accounts for the time devoted to sensory processing, motor preparation, and motor output, and a starting point parameter ($z$) accounts for any predispositions in the initial decision variable towards either boundary.

We analyzed the data using the HDDM Python toolbox [@wiecki2013hddm], which implements the RLDDM and uses a hierarchical Bayesian approach to compute the posterior distribution of group and individual parameters [for a detailed description of the model, see @pedersen2020simultaneous]. The Bayesian posterior estimations of the RLDDM rely on informative priors obtained from a prior meta-analysis [@wiecki2013hddm] for the DDM aspect of the model. On the other hand, non-informative broad normal distributions, centered at 0.5 after transformation, are used for the learning rate parameters (positive and negative).


\pagebreak

## Biased choices

We examined the PRL blocks where a food image was paired with a neutral image. 

```{r, message = FALSE, warning = FALSE, include = FALSE, results = "hide", echo=FALSE, cache=TRUE}
library("here")
library("tidyverse")
library("brms")
library("tidybayes")
library("scales")
library("ggthemes")
library("emmeans")
library("BayesFactor")
library("bayestestR")
library("crayon")  # for terminal colors
library("patchwork")
library("insight")
library("see")

library("cmdstanr")
cmdstan_version()

library("tidylog") # Load tidylog after dplyr and/or tidyr


# Increase max print
options(max.print = .Machine$integer.max)

source(here::here("src", "R", "functions", "funs_prl.R"))
source(here::here("src", "R", "functions", "funs_consecutive_trial_analysis.R"))

# Read data ---

# Read list of subjects used in the hDDMrl analysis.
lookup_tbl <- rio::import(
  here::here("data", "processed", "prl", "input_for_hddmrl", 
             "hddm_look_up_table_v3.csv")
)

# Read complete raw data.
d1 <- gen_data_for_consecutive_trial_analysis()

# Recode levels diag_cat.
d1$diag_cat <- 
  dplyr::recode(
    d1$diag_cat,
    "AN" = "AN",
    "BN" = "BN",
    "HC" = "HC",
    "RI" = "RI",
    "BN_R" = "RI",
    "AN_R" = "RI"
  )
d1$diag_cat <- factor(d1$diag_cat)

d <- d1 |>
  dplyr::rename(
    subj_code = subj_name
  )

# d |> 
#   group_by(diag_cat) |> 
#   summarize(
#     n_distinct(subj_code)
#   )
# 1 AN                            37
# 2 BN                            12
# 3 HC                           212
# 4 RI                            41

dat <- d 

# Examine the proportions of is_target_img_chosen in the 3 groups.

# Recode variables.

# Diagnostic category -> di (reference: HC)
dat$di <- factor(dat$diag_cat)
dat$di <- relevel(dat$di, ref = "HC")
contrasts(dat$di)

# Stimulus type
dat$st <- factor(dat$stimulus_type)
dat$st <- relevel(dat$st, ref = "neutral")
contrasts(dat$st)

# Is target image chosen
dat$trg_chosen <- dat$is_target_img_chosen
unique(dat$trg_chosen)
# [1] 0 1

# Subject id.
dat$ID <- factor(dat$subj_code)
length(unique(dat$ID))
# [1] 261

# RTs in sec.
dat <- dat |> 
  mutate(
    rt = rt1 / 1000
  ) |> 
  dplyr::filter(rt > 0.2 & stimulus_type == "food")


# By-subject data ---

# Computer one proportion for each condition/subject.
bysubj_freq <- dat |> 
  group_by(di, ID) |> 
  summarize(
    y = mean(trg_chosen)
  )
bysubj_freq |> 
  as.data.frame()

bysubj_freq$flag <- ifelse(
  (bysubj_freq$di == "HC") & (bysubj_freq$y < 0.3), NA, bysubj_freq$y
)

bysubj_freq <- bysubj_freq[complete.cases(bysubj_freq), ] 
bysubj_freq$flag <- NULL

hist(bysubj_freq$y)

```

The proportion of times the target image was chosen, for each group, is shown below.

```{r, echo=FALSE}
bysubj_freq |> 
  group_by(di) |> 
  summarise(
    m = mean(y, na.rm = TRUE)
  ) |> 
  kable(digits = 3)
```

\vspace{5mm}

The proportions were analyzed with a robust Bayesian regression model (a Beta model produced similar results).

\vspace{5mm}

```{r, message=FALSE, warning=FALSE, cache=TRUE}
priors <- c(
  set_prior("student_t(4, 0, 2.5)", class = "b")
)

bmod_02 <- brm(
  bf(y ~ di, sigma ~ di),
  data = bysubj_freq,
  family = student(),
  control = list(adapt_delta = 0.99),
  prior = priors,
  backend = "cmdstan",
  warmup = 1000,
  iter = 5000,
  cores = parallel::detectCores(),
  seed = "12345",
  chains = 4,
  refresh = 0,
  silent = TRUE
)
```


### Posterior predictive check

```{r, echo=FALSE}
pp_check(bmod_02) + 
  theme_cowplot()
```

\vspace{5mm}

### Model's coefficients

The estimations obtained for the model are summarized in Table below, which includes the mean, the standard error, and the lower and upper bounds of the 95% credible interval of the posterior distribution for each parameter. 

```{r, message=FALSE, warning=FALSE, echo=FALSE}
tidy(bmod_02, effect="fixed", conf.method="HPDinterval", prob = 0.95) |>
  dplyr::select("term", "estimate", "std.error", "conf.low", "conf.high") |>
   kable(digits = 3)
```

\vspace{5mm}

Contrasts were obtained with the `emmeans` function of the `emmeans` package:

\vspace{5mm}

```{r, message=FALSE, warning=FALSE, echo=FALSE}
emmeans::emmeans(bmod_02, ~ di,
                 regrid = "response") %>% 
  contrast(method = "revpairwise") |>
   kable(digits = 3)
```

\pagebreak

## Comorbidity

Individuals with eating disorders are prone to exhibiting not only eating-related pathologies, but also other comorbidities like mood and anxiety disorders. Here, we report the outcomes of the application of model M7 to the patient data, wherein patients were categorized into two groups based on the presence or absence of comorbidities. 

```
m = hddm.HDDMrl(
    data,
    depends_on={
        "a": ["diag_cat", "comorbidity", "stim"],
        "v": ["diag_cat", "comorbidity", "stim"],
        "t": ["diag_cat", "comorbidity", "stim"],
        "alpha": ["diag_cat", "comorbidity", "stim"],
        "pos_alpha": ["diag_cat", "comorbidity", "stim"],
    },
    dual=True,  
    p_outlier=0.05,
    informative=True
)
```

In each instance, the 95% credibility interval encompassed zero, thus indicating a lack of credible evidence for any differences in the RLDDM parameters between patients with and without comorbid diagnoses.

### Parameter $a$

For anorexic patients, the difference in the posterior estimates of the $a$ parameter for the two groups, $a_{\text{comorbidity present}} - a_{\text{comorbidity absent}}$, was 0.050, 95% CI [-0.124, 0.220] in the "food" condition; the difference in the posterior estimates of the $a$ parameter for the two groups, $a_{\text{comorbidity present}} - a_{\text{comorbidity absent}}$, was 0.097, 95% CI [-0.072, 0.256] in the "neutral" condition.

For bulimic patients, the difference in the posterior estimates of the $a$ parameter for the two groups, $a_{\text{comorbidity present}} - a_{\text{comorbidity absent}}$, was 0.116, 95% CI [-0.195, 0.396] in the "food" condition; the difference in the posterior estimates of the $a$ parameter for the two groups, $a_{\text{comorbidity present}} - a_{\text{comorbidity absent}}$, was 0.065, 95% CI [-0.258, 0.382] in the "neutral" condition.

### Parameter $\alpha^-$

For anorexic patients, the difference in the posterior estimates of the $\alpha^-$ parameter for the two groups, $\alpha^-_{\text{comorbidity present}} - \alpha^-_{\text{comorbidity absent}}$, was -2.071, 95% CI [-6.738, 2.446] in the "food" condition; the difference in the posterior estimates of the $a$ parameter for the two groups, $\alpha^-_{\text{comorbidity present}} - \alpha^-_{\text{comorbidity absent}}$, was 0.195, 95% CI [-4.514, 4.900] in the "neutral" condition.

For bulimic patients, the difference in the posterior estimates of the $\alpha^-$ parameter for the two groups, $\alpha^-_{\text{comorbidity present}} - \alpha^-_{\text{comorbidity absent}}$, was 1.357, 95% CI [-5.061, 7.299] in the "food" condition; the difference in the posterior estimates of the $a$ parameter for the two groups, $\alpha^-_{\text{comorbidity present}} - \alpha^-_{\text{comorbidity absent}}$, was 1.457, 95% CI [-4.393, 7.366] in the "neutral" condition.

### Parameter $\alpha^+$

For anorexic patients, the difference in the posterior estimates of the $\alpha^+$ parameter for the two groups, $\alpha^+_{\text{comorbidity present}} - \alpha^+_{\text{comorbidity absent}}$, was 0.429, 95% CI [-3.261, 4.326] in the "food" condition; the difference in the posterior estimates of the $a$ parameter for the two groups, $\alpha^+_{\text{comorbidity present}} - \alpha^+_{\text{comorbidity absent}}$, was 0.823, 95% CI [-3.273, 5.345] in the "neutral" condition.

For bulimic patients, the difference in the posterior estimates of the $\alpha^+$ parameter for the two groups, $\alpha^+_{\text{comorbidity present}} - \alpha^+_{\text{comorbidity absent}}$, was 1.674, 95% CI [-3.723, 7.396] in the "food" condition; the difference in the posterior estimates of the $a$ parameter for the two groups, $\alpha^+_{\text{comorbidity present}} - \alpha^+_{\text{comorbidity absent}}$, was 1.080, 95% CI [-4.487, 6.337] in the "neutral" condition.

\pagebreak

# References

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
\setlength{\parskip}{8pt}
\noindent

